Merge biotime timeseries with trait data

### 2022-09-19 analysis/01_filter_by_traits.Rmd
add models to the actual sensitivity script
This is what I really mean, it doesn't effect the final dataset though because all the studies I accidentally excluded were super low richness

#studies to include, since they meet the coverage requirement 
inc_coverage <- coverage %>% filter(perc > percent)

@@

#save locally and in cache
#usethis::use_data(study_table)
```

>>>>

#studies to include, since they meet the coverage requirement 
inc_coverage <- coverage %>% filter(perc >= percent)

@@

#save locally and in cache
usethis::use_data(study_table)
```
